Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-29 paper.tex
Formatting and add dictionary source

Needless to say, with every unregulated system comes abuse and piracy is no exception.
On top of that, piracy, on an individual level, is extremely difficult to combat because
of the immaterial nature of the items that would need to be protected. Ideas flow freely
between people especially when the Internet is involved, so stopping this flow becomes an
exponentially more difficult problem the more people have the restricted data. The ease
with which ideas propagate lead people like Thomas Jefferson to claim that they are
\enquote{incapable of confinement or exclusive appropriation.} Consequently, two parties form:
those that support piracy for its free and open spread of all information and those that
see piracy as a threat to the further advancement of technology and ideas.

Before proceeding further into the issue of piracy, it is important to have a grasp of
what piracy means insofar as how this paper interprets it. The dictionary defines piracy
as \enquote{the unauthorized use of another's production, invention, or conception especially in
infringement of a copyright.} While this covers the technical definition of piracy, this
paper elects to utilize a more wholistic definition. Piracy not only includes the
unauthorized use of someone's work, but it includes the tools and techniques that are
commonly used to accomplish this task such as torrent trackers, VPNs, and torrent clients.

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed
to continue to learn more about God's creation without being bound by their
financial status. Just as how someone can go to the library and checkout any
book that tickles their fancy, they should be freely able to learn from the
ongoing research of our world. Of course one should recognize that not all
information is safe or helpful to be freely available on the internet, but that
is a topic for a later section.

@@

Medical journals are not the only source of information that can sit behind a paywall.
Sometimes, as in the previous case, there is information that one might argue is unjustly
kept away from the common man. What one considers to be unjust is subjective, but the idea
is that piracy is a tool that consumers can employ to fight systems that they deem to be
unjust. Without piracy, one might have to roll over and accept their limited access or
resort to a more extreme and likely illegal approach. To put it another way, piracy acts
as a check on businesses to discourage them from integrating unpopular, anti-consumer
practices into their business model. When a consumer wants to purchase something and they
cannot afford it, they might start to look for alternative way of obtaining it. But, when
they can afford it and they think it is fairly priced, they will purchase it. Thus, piracy
is often where tech-savvy persons turn to when they need something that they feel is
exorbitantly priced, but is not often utilized when they feel the purchase is worthwhile.
This way, piracy acts as a safeguard for consumers when they feel they are being taken
advantage of by predatory business practices.
% XXX the statements in the paragraph above are largely unsubstantiated >:D
% XXX add darnton:pirating-and-publishing and bohannon:everyone sources if needed

@@

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed.
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by \citeauthor{mezzour:empirical-study} reveals that
piracy is not equal around the globe, and it poses serious problems especially
for people in poor countries where piracy is widespread. Although they
hypothesized, like other researchers, that \enquote{cyber criminals would target
rich countries} because of monetary incentives, they found that, cyber criminals
targeted \textcquote{mezzour:empirical-study}[.]{%
  poor countries in Sub-Saharan Africa because of the low cost of attacking
  computers in this region%
} \citeauthor{mezzour:empirical-study} concludes that, due to the high
correlation between piracy and malware, one of the policy implications is that
Sub-Saharan Africa requires reducing piracy to combat the spread of malware.
In more recent news, Antivirus provider Kaspersky recently uncovered an example
of malware spreading through pirated software.~\cite{pcmag:malware}

@@

The issue of trust is one that should not be unfamiliar to Christians. As
Christians, we have a Lord that we can trust in with all our hearts (Prov. 3:5).
As the Psalmist writes, \enquote{It is better to take refuge in the Lord than
to trust in man} (Ps. 118:8). Christians should be slow to put their entire
trust in metrics like those provided by \emph{ThePirateBay}; while they provide
some founts of trust, they should not immediately encourage Christians to trust
piracy.

>>>>

Needless to say, with every unregulated system comes abuse and piracy is no exception.
On top of that, piracy, on an individual level, is extremely difficult to combat because
of the immaterial nature of the items that would need to be protected. Ideas flow freely
between people especially when the Internet is involved, so stopping this flow becomes an
exponentially more difficult problem the more people have the restricted data. The ease
with which ideas propagate lead people like Thomas Jefferson to claim that they are
\textcquote{barlow:wine}[.]{incapable of confinement or exclusive appropriation}
Consequently, two parties form: those that support piracy for its free and open spread
of all information and those that see piracy as a threat to the further advancement of
technology and ideas.

Before proceeding further into the issue of piracy, it is important to have a grasp of
what piracy means insofar as how this paper interprets it. The dictionary defines piracy
as \textcquote{merriam-webster:piracy}[.]{%
  the unauthorized use of another's production, invention, or conception
  especially in infringement of a copyright%
} While this covers the technical definition of piracy, this paper elects to utilize a
more wholistic definition. Piracy not only includes the unauthorized use of someone's
work, but it includes the tools and techniques that are commonly used to accomplish
this task such as torrent trackers, VPNs, and torrent clients.

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed to
continue to learn more about God's creation without being bound by their financial status.
The Bible encourages one to pursue knowledge. Proverbs 1:5 reads,
\textquote[][.]{%
  \textins{l}et the wise hear and increase in learning, and the one who
  understands obtain guidance%
}
One's ability to live out this verse should not be artificially hindered by financial
station. Just as how someone can go to the library and checkout any book that tickles
their fancy, they should be freely able to learn from the ongoing research of our world.
Of course one should recognize that not all information is safe or helpful to be freely
available on the internet, but that is a topic for a later section.

@@

Medical journals are not the only source of information that can sit behind a paywall.
Sometimes, as in the previous case, there is information that one might argue is unjustly
kept away from the common man. What one considers to be unjust is subjective, but the idea
is that piracy is a tool that consumers can employ to fight systems that they deem to be
unjust. Without piracy, one might have to roll over and accept their limited access or
resort to a more extreme and likely illegal approach. To put it another way, piracy acts
as a check on businesses to discourage them from integrating unpopular, anti-consumer
practices into their business model. When a consumer wants to purchase something and they
cannot afford it, they might start to look for alternative way of obtaining it. But, when
they can afford it and they think it is fairly priced, they will purchase it.

According to a survey conducted by MUSO, \textcquote{muso:about}[,]{%
  a data company that provides the most complete and trusted view of global
  piracy and unlicensed media consumption%
} the most common reasons that users pirate is \textcquote{vice:pirates}[.]{%
  the content they were looking for wasn’t legally available (34 percent) was
  too cumbersome or difficult to access (34 percent), or wasn’t affordable
  (35 percent)%
} The reason most people pirate is not that they are not willing to pay for the content,
but that they cannot legally obtain it any other way, that it was too hard to access, or
that it was not affordable. In the latter two cases, one can see the consumer's power to
protest poorly designed systems or unaffordable prices. Thus, piracy is often where
tech-savvy persons turn to when they need something that they feel is exorbitantly priced,
but is not often utilized when they feel the purchase is worthwhile. This way, piracy
acts as a safeguard for consumers when they feel they are being taken advantage of by
predatory business practices.

@@

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed.
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by \citeauthor{mezzour:empirical-study} reveals that
piracy is not equal around the globe, and it poses serious problems especially
for people in poor countries where piracy is widespread. Although they
hypothesized, like other researchers, that \textquote{cyber criminals would target
rich countries} because of monetary incentives, they found that, cyber criminals
targeted \textcquote{mezzour:empirical-study}[.]{%
  poor countries in Sub-Saharan Africa because of the low cost of attacking
  computers in this region%
} \citeauthor{mezzour:empirical-study} concludes that, due to the high
correlation between piracy and malware, one of the policy implications is that
Sub-Saharan Africa requires reducing piracy to combat the spread of malware.
In more recent news, Antivirus provider Kaspersky recently uncovered an example
of malware spreading through pirated software.~\cite{pcmag:malware}

@@

The issue of trust is one that should not be unfamiliar to Christians. As
Christians, we have a Lord that we can trust in with all our hearts (Prov. 3:5).
As the Psalmist writes, \textquote{It is better to take refuge in the Lord than
to trust in man} (Ps. 118:8). Christians should be slow to put their entire
trust in metrics like those provided by \emph{ThePirateBay}; while they provide
some founts of trust, they should not immediately encourage Christians to trust
piracy.
